---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# `{nrv.forsite.app}`

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Installation

You can install the development version of `{nrv.forsite.app}` like so:

```{r}
pak::pkg_install("FOR-CAST/nrv-forsite-app")
```

## Run

You can launch the application by running:

```{r, eval = FALSE}
nrv.forsite.app::run_app()
```

## Development

This app is built using the [`golem`](https://thinkr-open.github.io/golem/index.html) framework.
Before making contributions, please familiarize yourself with that package:

2. [Development with `{golem}`](https://thinkr-open.github.io/golem/articles/b-develop.html);
3. [Deployment](https://thinkr-open.github.io/golem/articles/c-deploy.html);

## About

You are reading the doc about version : `r golem::pkg_version()`

This README has been compiled on the

```{r}
Sys.time()
```

Here are the tests results and package coverage:

```{r, error = TRUE}
devtools::check(quiet = TRUE)
```

```{r echo = FALSE}
unloadNamespace("nrv.forsite.app")
```

```{r, error = TRUE}
covr::package_coverage()
```
